Finite-state morphological transducers for three Kypchak languages

### 2014-03-14 kipchak-lrec-2013/kipchak-paper.tex
ambiguous harmony
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@50739 72bbbca6-d526-0410-a7d9-f06f51895060

%FIXME: description of each one, with examples
\begin{itemize}
 \item \textbf{Ambiguous and `irregular' harmony}: In Tatar, certain characters in the alphabet which represent vowels can be 
   ambiguous between front vowels, such as е. For example: дәрес `lesson', дәресләр `lessons'; ел `year', 
   еллар `years'. 
 \item \textbf{Loan words}: The character ё in Russian words is pronounced as /jo/ where in native Kumyk words 
   it represents the sound /ø/. These two pronunciations will select for different suffixes, /jo/ taking
   back vowel suffixes самолётлар `aeroplanes', and /ø/ taking front vowel suffixes сёзлер `words'.
 \item \textbf{Acronyms and numerals}: Acronyms and numerals are challenging as they will often be pronounced out loud
   in their non-abbreviated forms, for example in Kazakh, 30-дан `from thirty', 5-тен `from 5'. The ablative
   suffix -DAn alters for the phonology, but in the numeral string there is no indication of how they should alter.
\end{itemize}

>>>>

%FIXME: description of each one, with examples
\begin{itemize}
 \item \textbf{Ambiguous and `irregular' harmony}: In Tatar, certain characters in the alphabet which represent vowels can be 
   ambiguous between a vowel and a 'yoticised' vowel, such as е. For example: дәрес `lesson', дәресләр `lessons'; ел `year', 
   еллар `years'. 
 \item \textbf{Loan words}: The character ё in Russian words is pronounced as /jo/ where in native Kumyk words 
   it represents the sound /ø/. These two pronunciations will select for different suffixes, /jo/ taking
   back vowel suffixes самолётлар `aeroplanes', and /ø/ taking front vowel suffixes сёзлер `words'.
 \item \textbf{Acronyms and numerals}: Acronyms and numerals are challenging as they will often be pronounced out loud
   in their non-abbreviated forms, for example in Kazakh, 30-дан `from thirty', 5-тен `from 5'. The ablative
   suffix -DAn alters for the phonology, but in the numeral string there is no indication of how they should alter.
\end{itemize}
